\documentclass[openany, oneside]{book}

% \input{preamble}
% \input{Russian}

% \newcommand{\vf}{\vspace{5mm}}

\usepackage{tgschola}
\usepackage{euscript}
\usepackage{graphicx}

\usepackage{epigraph}

\usepackage{geometry}
\geometry{a4paper, top=30mm, left=30mm, right=30mm, bottom=35mm}

\renewcommand{\epigraphsize}{\normalsize}
\renewcommand{\footnotesize}{\normalsize}

% \hyphenpenalty = 10000
% \fontdimen2\font=0.7ex
% \fontdimen3\font=0.4em
\renewcommand{\baselinestretch}{1.015}

\sloppy
\begin{document}

\thispagestyle{empty}

\phantom{}

\begin{center}
\vspace{4cm}
\hrule height 1pt
\vspace{1cm}
\scalebox{4.8}{$\EuScript{DREAMCATCHER}$}\\
\vspace{1cm}
\hrule height 1pt
\vspace{1cm}
\scalebox{1.5}{A science fiction story}
\end{center}

\pagebreak

\chapter*{Prologue}

Dreams are elusive, mysterious things. You can reach the heights of love in a dream, or see the world around you crumble into dust. You can answer Humanity's biggest questions without effort, but then you always wake up, curse the annoying alarm app on your phone, and step into another day of mundane events, as if nothing happened. The fleeting memory of something grand and surreal lingers warmly in your mind, and you watch it fade away, amused at how it could ever make sense to your delirious brain.\\

Ludwig was also dreaming, on a cold winter night in Norway, and he was quite enjoying a simple tuna sandwich, cuddled in an armchair near a burning hearth. Oh, but the world is unfair! He would have to wake up, put on warm clothes, and leave his friendly home to get to school before dawn, parsing through heaps of snow and squinting his eyes in the frosty wind.

He was halfway through the sandwich when a distant ringing sound echoed in the back of his consciousness, and a sense of dreadful realization came over him, became him, as he knew his simple world would cease to be. In its final moments, Ludwig's dream-self desired only closure --- only to \emph{finish the sandwich} before it was too late. Hurriedly he opened his mouth to take one last bite\ldots and found himself lying on his bed, his phone ringing and vibrating on the cupboard.
With a frustrated groan he reached his hand to silence the damn thing, but wait --- oh wonder! --- his hand was holding a half-eaten tuna sandwich!

Ludwig sat up straight in his bed, the last bits of sleepiness shedding from his mind, and gazed in astonishment at the innocent-looking sandwich, familiar and alien at the same time. He could contemplate the meaning of what had just occurred, and the impact it would have on the world, but he did what any sensible 9-year-old would do --- he ate the rest of the sandwich and began to pack his bag for school.\\

That night on February 6th of 2027 was the first documented case of \emph{reverse manifestation}, a miraculous occurrence where a person could, through sheer strength of will and intensity of emotion, \emph{push} a part of their dream-world out into reality, while still being asleep.\\

Here is a quick summary of the events that followed:

\begin{itemize}
  \item[Mar. 19, 2027:] In southern China, a man named Mao Yu was found floating gently above his bed, supposedly having a dream where he was flying.

  \item[Apr. 13, 2027:] 
\end{itemize}

Suffice it to say, the world took a long time to realize the danger and potential of reverse manifestation. The first incidents were very localized and harmless: people woke up to find things next to them that they had dreamt of. There were reported cases of people floating gently above their beds, supposedly having a dream where they were flying. And then there was one 26-year-old man in suburban Brazil who dreamt that all the plants on Earth were colored crimson-red instead of green. Shortly after, billions of people felt their hearts skip a beat when they saw forests, jungles, groves, bushes, lawns, and house plants turn red from top to bottom, as if someone were pouring old, viscous blood on them. One could say is was like Autumn, but that particular shade of red had never been seen on plants before. It looked unnatural, yet not artificial, with a tint of alien malice. In a children's horror story, the monster hiding in a dark cave would have eyes colored in that same shade of crimson-red.\\

Many were so astounded by this change that for hours they could not stop looking at these red leaves, driven by the same instinct that makes one stare into a pair of predatory eyes in the dark, paralyzed by fear and unable to look away. But the very next day works began all over the world to contain the threat of reverse manifestation. Surely, if you could change the molecular structure of plants, you could also kill someone in your sleep? Make an entire city disappear? Or, for that matter, change the very laws of physics? No-one knew the limits to which someone's sick and violent dream-reality could manifest into the real world.\\

If course, the first priority was to 

\end{document}
